### 2022-06-07 README.Rmd
typo enmac link
move things to ebike
imob validation and batch test

See vignette [ENMAC scenario](articles/1_enmac_scenario.html) to see how this was modeled.

@@

Use of [CyclingStreets.net](https://cyclinstreets.net) ([R package](https://rpackage.cyclestreets.net/)) for fast and quiet bike routes for baseline scenario.  
For e-bike scenario, we developed a proper algorithm, considering the topography (and [`slopes`](https://docs.ropensci.org/slopes) package).

>>>>

See vignette [ENMAC scenario](articles/1_emnac_scenario.html) to see how this was modeled.

@@

Use of [CyclingStreets.net](https://cyclinstreets.net) ([R package](https://rpackage.cyclestreets.net/)) for fast and quiet bike routes for baseline scenario.

For e-bike scenario, we developed a proper algorithm, considering the topography, and using  [`slopes`](https://docs.ropensci.org/slopes) package.
